---
title: "R-Output Presentation"
author: "Chenghui Zheng"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(MASS)
library(tidyverse)
library(ggplot2)
library(cowplot)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
locoall1 <- read.csv("r_output/simulation_locoall1.csv")
lococv1 <- read.csv("r_output/simulation_lococv1.csv")
locosp1 <- read.csv("r_output/simulation_locosp1.csv")
lococv2 <- read.csv("r_output/simulation_lococv2.csv")
locoall2 <- read.csv("r_output/simulation_locoall2.csv")
locosp2 <- read.csv("r_output/simulation_locosp2.csv")

locosp3 <- read.csv("r_output/simulation_locosp3.csv")
locoall3 <- read.csv("r_output/simulation_locoall3.csv")
locosp4 <- read.csv("r_output/simulation_locosp4.csv")
locoall4 <- read.csv("r_output/simulation_locoall4.csv")


```

### (a) Linear Model with Independent Predictors

\[ Y_1 \sim 1.5X_1 +1.5 X_2 + 2X_3 + 2X_4 + 2X_5 + 3X_6 + 4X_7 + 5X_8 + \epsilon \]

### (b) Linear Model with Correlated Predictors

\[ Y_2 \sim 1.5X_1 +1.5 X_2 + 2X_3 + 2X_4 + 2X_5 + 3X_6 + 4X_7 + 5X_8 + \epsilon \]

Where \(X_1 \not\perp\!\!\!\perp X_2\) and \(\text{cov}(X_1, X_2) = 0, 0.5, 0.75, 0.9\) respectively.

### (c) Linear Model with Correlated Predictors and Different SNR

\[ Y_3 \sim 1.5X_1 +1.5 X_2 + 2X_3 + 2X_4 + 2X_5 + 3X_6 + 4X_7 + 5X_8 + \epsilon \]

Where \(\text{cov}(X_i, X_j) = \rho^{|i-j|}\) and \(\epsilon \sim N(0, \sigma^2)\) with \(\sigma^2 = 0.1, 0.5, 0.75, 2.1\).

### (d) Non-linear Model 

\[ Y_4 \sim 2X_1^2 + 2\cos(4X_2) + \sin(X_3) + \exp\left(\frac{X_4}{3}\right) + 3X_5 X_6 + 5 X_7 + \max(0, X_8) \]


## LOCO only
```{r,echo=FALSE,warning=FALSE,message=FALSE}
locoall1$Features <- factor(locoall1$Features, levels = paste0("X", 1:20))
plall11 <- ggplot(locoall1, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
plall12 <- ggplot(locoall1, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 2) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

lococv1$Features <- factor(lococv1$Features, levels = paste0("X", 1:20))
plcv11 <- ggplot(lococv1, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plcv12 <- ggplot(lococv1, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 2) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

locosp1$Features <- factor(locosp1$Features, levels = paste0("X", 1:20))
plsp11 <- ggplot(locosp1, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plsp12 <- ggplot(locosp1, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 2) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()


#plot_grid(plall12, plsp12,plcv12, labels = "AUTO")
```





```{r,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE}
loco1$Features <- factor(loco1$Features, levels = paste0("X", 1:20))
pl1 <- ggplot(loco1, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue')  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
pl1
```

```{r,echo=FALSE,warning=FALSE,message=FALSE, eval=FALSE}
loco1$Features <- factor(loco1$Features, levels = paste0("X", 1:20))
 pl11 <- ggplot(loco1, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue')  +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averagd P.value') +
  theme_minimal() 

```



```{r,echo=FALSE,warning=FALSE,message=FALSE}
locoall2$Features <- factor(locoall2$Features, levels = paste0("X", 1:20))
locoall2$Correlation <- as.factor(locoall2$Correlation)
plall21 <- ggplot(locoall2, aes(x = Features, y = P.Value, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1") +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
plall22 <- ggplot(locoall2, aes(x = Features, y = Feature_Importance_Score,color = Correlation)) +
  geom_point(size = 2) +
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1")  +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

lococv2$Features <- factor(lococv2$Features, levels = paste0("X", 1:20))
lococv2$Correlation <- as.factor(lococv2$Correlation)
plcv21 <- ggplot(lococv2, aes(x = Features, y = P.Value,color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plcv22 <- ggplot(lococv2, aes(x = Features, y = Feature_Importance_Score,color =Correlation)) +
  geom_point( size = 2)+
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

locosp2$Features <- factor(locosp2$Features, levels = paste0("X", 1:20))
locosp2$Correlation <- as.factor(locosp2$Correlation)
plsp21 <- ggplot(locosp2, aes(x = Features, y = P.Value,color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plsp22 <- ggplot(locosp2, aes(x = Features, y = Feature_Importance_Score,color =Correlation)) +
  geom_point( size = 2)+
  geom_line(aes(group = Correlation), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case b): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

#plot_grid(plall21, plsp21,plcv21,labels = "AUTO")
#plot_grid(plall22, plsp22,plcv22, labels = "AUTO")

```



```{r,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE}
loco2$Features <- factor(loco2$Features, levels = paste0("X", 1:20))
loco2$Correlation <- as.factor(loco2$Correlation)
 pl22 <- ggplot(loco2, aes(x = Features, y = P.Value, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal() 




```


```{r,echo=FALSE,warning=FALSE,message=FALSE}
#plot_grid(pl1, pl2, labels = "AUTO")
```


```{r,echo=FALSE,warning=FALSE,message=FALSE}
locoall3$Features <- factor(locoall3$Features, levels = paste0("X", 1:20))
locoall3$snr <- as.factor(locoall3$snr)
plall31 <- ggplot(locoall3, aes(x = Features, y = P.Value, color = snr)) +
  geom_point(size = 3) +
  geom_line(aes(group = snr), size = 1) +
  scale_color_brewer(palette = "Set1") +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
plall32 <- ggplot(locoall3, aes(x = Features, y = Feature_Importance_Score,color = snr)) +
  geom_point(size = 2) +
  geom_line(aes(group = snr), size = 1) +
  scale_color_brewer(palette = "Set1")  +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

locosp3$Features <- factor(locosp3$Features, levels = paste0("X", 1:20))
locosp3$snr <- as.factor(locosp3$snr)
plsp31 <- ggplot(locosp3, aes(x = Features, y = P.Value,color = snr)) +
  geom_point(size = 3) +
  geom_line(aes(group = snr), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plsp32 <- ggplot(locosp3, aes(x = Features, y = Feature_Importance_Score,color =snr)) +
  geom_point( size = 2)+
  geom_line(aes(group = snr), size = 1) +
  scale_color_brewer(palette = "Set1") + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
#plot_grid(plall31, plsp31, labels = "AUTO")
#plot_grid(plall32, plsp32, labels = "AUTO")
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE}
loco3$Features <- factor(loco3$Features, levels = paste0("X", 1:20))
loco3$snr <- as.factor(loco3$snr)
pl33 <- ggplot(loco3, aes(x = Features, y = P.Value, color = snr)) +
  geom_point(size = 3) +
  geom_line(aes(group = snr), size = 1)+
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

```



```{r,echo=FALSE,warning=FALSE,message=FALSE}
locoall4$Features <- factor(locoall4$Features, levels = paste0("X", 1:20))
plall41 <- ggplot(locoall4, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
plall42 <- ggplot(locoall4, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 2) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()

locosp4$Features <- factor(locosp4$Features, levels = paste0("X", 1:20))
plsp41 <- ggplot(locosp4, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")  +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

plsp42 <- ggplot(locosp4, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 2) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0, linetype = "dashed", color = "green")  +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()


plall11
plall21
plall31
plall41

plsp11
plsp21
plsp31
plsp41

plot_grid(plall12,plall22,plall32,plall42, labels = "AUTO")
plot_grid(plsp12,plsp22,plsp32,plsp42, labels = "AUTO")
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE}
loco4$Features <- factor(loco4$Features, levels = paste0("X", 1:20))
pl44 <- ggplot(loco4, aes(x = Features, y = P.Value)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()

```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
#plot_grid(pl11,pl22, labels = "AUTO")
```

## GCM filter only
```{r,echo=FALSE}
gcm1 <- read.csv("r_output/simulation_gcm_filter1.csv")
gcm2 <- read.csv("r_output/simulation_gcm_filter2.csv")
gcm3 <- read.csv("r_output/simulation_gcm_filter3.csv")
gcm4 <- read.csv("r_output/simulation_gcm_filter4.csv")

```

```{r,echo=FALSE}
gcm1$Features <- factor(gcm1$Features, levels = paste0("X", 1:20))
pla <- ggplot(gcm1, aes(x = Features, y = p.val)) +
  geom_point(color = 'blue', size = 1) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")+
  geom_hline(yintercept = 0.01, linetype = "dashed", color = "green") +
  labs(title = 'Case a): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
pla

```

```{r, echo=FALSE}
gcm2$Features <- factor(gcm2$Features, levels = paste0("X", 1:20))
gcm2$Correlation <- as.factor(gcm2$Correlation)
plb <- ggplot(gcm2, aes(x = Features, y = p.val, color = Correlation)) +
  geom_point(size = 1) +
  geom_line(aes(group = Correlation), size = 1)+
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")+
  geom_hline(yintercept = 0.01, linetype = "dashed", color = "green") +
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case b):',
       x = 'Features',
       y = 'Averaged P.value') +
  theme_minimal()
plb


gcm3$Features <- factor(gcm3$Features, levels = paste0("X", 1:20))
gcm3$snr <- as.factor(gcm3$snr)
plc <- ggplot(gcm3, aes(x = Features, y = p.val, color = snr)) +
  geom_point(size = 1) +
  geom_line(aes(group = snr), size = 1)+
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")+
  geom_hline(yintercept = 0.01, linetype = "dashed", color = "green")+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
plc

gcm4$Features <- factor(gcm4$Features, levels = paste0("X", 1:20))
pld <- ggplot(gcm4, aes(x = Features, y = p.val)) +
  geom_point(color = 'blue', size = 1) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")+
  geom_hline(yintercept = 0.01, linetype = "dashed", color = "green") +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Averaged P.Value') +
  theme_minimal()
pld
```
\pagebreak

```{r,echo=FALSE}
cut_gcm1 <- gcm1 %>% filter(p.val<0.01)%>%arrange(p.val) %>% mutate(rank=rank(p.val))

a<- ggplot(cut_gcm1, aes(x = Features, y = rank)) +
  geom_point(color = 'blue', size = 1) +
  geom_line(aes(group = 1), color = 'blue') +
  labs(title = 'Case a): ') +
  theme_minimal()
  
cut_gcm2 <- gcm2 %>% filter(p.val<0.01)%>%arrange(Correlation, p.val) %>% group_by(Correlation)%>% mutate(rank=rank(p.val))
  
b<- ggplot(cut_gcm2, aes(x = Features, y = rank, color = Correlation)) +
  geom_point(color = 'blue', size = 1) +
 geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case b):' ) +
  theme_minimal()
  
  cut_gcm3 <- gcm3 %>% filter(p.val<0.01)%>%arrange(snr, p.val) %>%group_by(snr)%>% mutate(rank=rank(p.val))
c<-  ggplot(cut_gcm3, aes(x = Features, y = rank, color = snr)) +
  geom_point(color = 'blue', size = 1) +
 geom_line(aes(group = snr), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c):' ) +
  theme_minimal()
 
 cut_gcm4 <- gcm4 %>% filter(p.val<0.01)%>%arrange(p.val) %>% mutate(rank=rank(p.val))
 d<- ggplot(cut_gcm4, aes(x = Features, y = rank)) +
  geom_point(color = 'blue', size = 1) +
  geom_line(aes(group = 1), color = 'blue') +
  labs(title = 'Case d): ') +
  theme_minimal()
 
plot_grid(a,b,c, d, labels = "AUTO")
```





## GCM filter first + LOCO
```{r,echo=FALSE,eval = FALSE}
alg1 <- read.csv("r_output/simulation_alg1.csv")
alg2 <- read.csv("r_output/simulation_alg2.csv")
alg3 <- read.csv("r_output/simulation_alg3.csv")
alg4 <- read.csv("r_output/simulation_alg4.csv")
```

```{r,echo=FALSE,eval=FALSE}
alg1$Features<-factor(alg1$Features, levels = paste0("X", 1:20))
pl1 <- ggplot(alg1, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_errorbar(aes(ymin = LB, ymax = UB), width = 0.2, color = 'black') +
  labs(title = 'Case a):',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
pl1

alg2$Features <- factor(alg2$Features, levels = paste0("X", 1:20))
alg2$Correlation <- as.factor(alg2$Correlation)
pl2 <-ggplot(alg2, aes(x = Features, y = Feature_Importance_Score, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case b):',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
pl2 
```

```{r,echo=FALSE,eval=FALSE}
alg1$Features<-factor(alg1$Features, levels = paste0("X", 1:20))
pl1 <- ggplot(alg1, aes(x = Features, y = Rank)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  labs(title = 'Case a):',
       x = 'Features',
       y = 'Averaged Rank') +
  theme_minimal()
pl1

alg2$Features <- factor(alg2$Features, levels = paste0("X", 1:20))
alg2$Correlation <- as.factor(alg2$Correlation)
pl2 <-ggplot(alg2, aes(x = Features, y = Rank, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case b):',
       x = 'Features',
       y = 'Averaged Rank') +
  theme_minimal()
pl2 
```

```{r,echo=FALSE, eval=FALSE}
alg3$Features <- factor(alg3$Features, levels = paste0("X", 1:20))
alg3$snr <- as.factor(alg3$snr)
pl3 <- ggplot(alg3, aes(x = Features, y = Feature_Importance_Score, color = snr)) +
  geom_point(size = 3) +
  geom_line(aes(group = snr), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
pl3
```

```{r,echo=FALSE,eval=FALSE}
alg3$Features <- factor(alg3$Features, levels = paste0("X", 1:20))
alg3$snr <- as.factor(alg3$snr)
pl3 <- ggplot(alg3, aes(x = Features, y = Rank, color = snr)) +
  geom_point(size = 3) +
  geom_line(aes(group = snr), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Averaged Rank') +
  theme_minimal()
pl3
```

```{r,echo=FALSE,eval=FALSE}
alg4$Features <- factor(alg4$Features, levels = paste0("X", 1:20))
pl4 <- ggplot(alg4, aes(x = Features, y = Feature_Importance_Score)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue') +
  geom_errorbar(aes(ymin = LB, ymax = UB), width = 0.2, color = 'black') +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Feature Importance Score') +
  theme_minimal()
pl4
```

```{r,echo=FALSE,eval=FALSE}
alg4$Features <- factor(alg4$Features, levels = paste0("X", 1:20))
pl4 <- ggplot(alg4, aes(x = Features, y = Rank)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue')  +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Averaged Rank') +
  theme_minimal()
pl4
```

```{r,echo=FALSE}
#plot_grid(pl1,pl2,pl3, pl4, labels = "AUTO")
```

\pagebreak
## GCM only
```{r,echo=FALSE,eval=FALSE}
gcm1 <- read.csv("r_output/simulation_gcm_loco1.csv")
gcm2 <- read.csv("r_output/simulation_gcm_loco2.csv")
gcm3 <- read.csv("r_output/simulation_gcm_loco3.csv")
gcm4 <- read.csv("r_output/simulation_gcm_loco4.csv")
feature <- c('X1', 'X2','X3','X4')
gcm1$Features <- feature
gcm2$Features <- feature
gcm3$Features <- rep(feature,times=4)
gcm4$Features <- rep(feature,times=4)

```

```{r,echo=FALSE,eval=FALSE}
pl1 <- ggplot(gcm1, aes(x = Features, y = Rejection_Rate)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue')+
  labs(title = 'Case a):',
       x = 'Features',
       y = 'Rejection_Rate') +
  theme_minimal()

pl2 <- ggplot(gcm2, aes(x = Features, y = Rejection_Rate)) +
  geom_point(color = 'blue', size = 3) +
  geom_line(aes(group = 1), color = 'blue')+
  labs(title = 'Case b):',
       x = 'Features',
       y = 'Rejection_Rate') +
  theme_minimal()

```

```{r,echo=FALSE}
#plot_grid(pl1, pl2, labels = "AUTO")
```

```{r,echo=FALSE,eval=FALSE}
gcm3$Correlation <- as.factor(gcm3$Correlation)
pl3 <- ggplot(gcm3, aes(x = Features, y = Rejection_Rate, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case c): ',
       x = 'Features',
       y = 'Rejection_Rate') +
  theme_minimal()
```

```{r,echo=FALSE,eval=FALSE}
gcm4$Correlation <- as.factor(gcm4$Correlation)
pl4 <- ggplot(gcm4, aes(x = Features, y = Rejection_Rate, color = Correlation)) +
  geom_point(size = 3) +
  geom_line(aes(group = Correlation), size = 1)+
  scale_color_brewer(palette = "Set1") +
  labs(title = 'Case d): ',
       x = 'Features',
       y = 'Rejection_Rate') +
  theme_minimal()
```

```{r,echo=FALSE,eval=FALSE}
plot_grid(pl1,pl2,pl3, pl4, labels = "AUTO")
```
\pagebreak
####################GCM Simulation###################################
```{r,echo=FALSE,eval=FALSE}
gcm_s1 <- read.csv("r_output/simulation_gcm1.csv")
gcm_s2 <- read.csv("r_output/simulation_gcm2.csv")
```

$$
a) Z \sim N(0,1), X = 2*sin(Z) + 0.1*N(0,1), Y = 2*sin(Z) + 0.1*N(0,1)
$$

```{r,echo=FALSE,eval=FALSE}

ggplot(gcm_s1, aes(x = Sample_Size, y = Rejection_Rate)) +
  geom_line() +
  geom_point() +
  labs(title = "Rejection Rate vs. Sample Size",
       x = "Sample Size",
       y = "Rejection Rate") +
  theme_minimal()
```
$$
b) Z \sim N(0,1), X = 2*Z + 0.1*N(0,1), Y = 2*Z + 0.1*N(0,1)
$$
```{r, echo=FALSE,eval=FALSE}
ggplot(gcm_s2, aes(x = Sample_Size, y = Rejection_Rate)) +
  geom_line() +
  geom_point() +
  labs(title = "Rejection Rate vs. Sample Size",
       x = "Sample Size",
       y = "Rejection Rate") +
  theme_minimal()

```

